\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/ld.tex
small change

\section{Formal development}
\label{sec:ld}
\TODO{Later, in implementation we can write that we use ABY for compiling intermediate to target also.}

\TODO{Use mult op instead of add? arguments of using arithmetic are clearer there; though we also use arithmetic always for add also. Or write both in exp and write rule for mul; how about bit-wise And? shifts?
Say that more exp written in implementation}

@@

\divya{Start here...}
\subsubsection*{Circuit semantics} The target semantics produces a
circuit to compute over the secret data using an MPC protocol. \nc{We use 2PC and MPC interchangeably. I guess its fine?}With
our circuit semantics, we model the \emph{functional} aspect of the
protocol, parametrized by the sharing functions.

>>>>

\section{Formal development}
\label{sec:ld}

@@

\divya{Start here...}
\subsubsection*{Circuit semantics} Evaluating a program in the intermediate language produces a
circuit over the secret data to be computed using an \mpc protocol in the distributed setting. With
our circuit semantics, we model the \emph{functional} aspect of a \mpc protocol, parametrized by the sharing functions.
